MLISA: Machine Learning-based \\ Intelligent Service Agents

### 2014-11-14 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

Web services are loosely-coupled business applications willing to cooperate in distributed settings within different groups called communities. Communities aim to provide web services with better visibility, efficiency, market share and total payoff. A number of mechanisms and models have been recently proposed to aggregate web
services and make them cooperate within their communities. However, the solutions mostly focus on short term goals and the decisions are optimized for short-term goals. Moreover, these solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion. In this paper, we propose a strategic decision making mechanism that regulates web service agents' decision making process in terms of cooperating with one another. This model first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. 
%Utilizing the training model, the decision making mechanism implements a decision tree with an estimation of long-term utility gain for the web services. Communities can used the trained model and instantly choose best-response strategies considering their long-term gain. 
Our findings show that communities of web services can efficiently find the appropriate web service to invite cooperating with them as well as a single web service can find best communities to target joining them. In further details, after being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. In contrast, communities can consider the training into account and analyze the characteristics of different individual web services and make prudent decisions while inviting a web service to join or accepting a join inquiry initiated from a web service. In general, MLISA equips web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore opting for best decision available. The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.

@@

\IEEEPARstart{O}{ver} the past years, online services have become important part of many scalable business applications. The increasing reliance on online service providers has significantly influenced the way web services are engineered. Therefore, given the dynamic and unpredictable nature of the Internet, delivering high quality services is still a critical and challenging issue. One practical solution that delivers high quality service is utilizing intelligent decision making agents. These agents are aimed at maximizing gain by exploring best ways of providing services that satisfy end users. However, agent-based web services are functionally limitted in the sense that they cannot handle large number of requests at the same time, otherwise their quality of provided service would diminish. The recent developments attempted to shift web services from passive model in the form of individual components to autonomous and group-based components that follow common goals. In group-based models, interaction, composition, and cooperation are the key challenges \cite{ICWS2011-1, SCC2011-1, journals/mags/BaldoniBM10, journals/jcss/CasadoYT13} that have direct impact on group's overall performance in achieving common goals. All that being said, the concept of \emph{community} of web services has been emerged that gathers services having similar functionality but distinct non-functional properties \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic, 10.1109/ARES.2008.7}. A \emph{community} of web service runs continuous performance assessment functions that regulate web services' interactions and manage their composition and cooperation.

The advantages of community of Web services is that the community facilitates the discovery of web services and as community provides better quality services compared to passive models with individual components. In other words, communities act as abstract web services, communicating with external entities via same standard protocols that a normal web services employs. But they regulate the service process via sophisticated internal communication protocols that result in providing a service out of combined work of a number of web services. The down side to communities is the management complexity that involves finding/inviting individual web services and managing the overall quality as combined work done by web services that although have similar functionality, but have different attitudes. Interacting with communities of web services, users send their requests to the coordinators of the community, which plays the role of the community representative or access point. The com munity coordinator in \emph{community centralized} architecture is responsible for task receive/delivery issues. Moreover, as community representative, it verifies credentials of new web services before accepting them to join the community as well as firing web services, which do not add enough value to the community.

Recent work have emphasized on motivation and benefits of communities of web services [references]. This is due to the fact that communities facilitate discovery of web services, improve the Quality of Service (QoS), and help individual services find better market share and opportunities. Now there is a twofold challenge that is still not addressed: (1) the first challenge is community development, which is finding the right web service for the community, satisfying all web services and community coordinators involved within the community; and (2) the second challenge is from individual web service side in the sense that a web service seeks for communities to interact with and obtain best outcome. Towards addressing these research problems, there have been a number of proposals. Some of these works propose complex models on demand algorithms \cite{DBLP:conf/IEEEscc/LimTMB12, 10.1109/TSC.2012.12, 10.1109/TSC.2014.2312940} to effectively find target points. But they have to simplify the algorithm by limited parameters in order to make it feasible and algorithm executable. Simplified problems some times negatively influence the outcome in the sense that simplifying the constraints may cause ignoring important aspects of the problem. For example \cite{10.1109/TSC.2012.12} proposes a simple egalitarian way of distributing gain, which completely ignores gain for collaborative work instead of complex shapely-value. This model considers gain for all subset of agents working together, which basically ignores the most important criteria of finding optimal group. Other category of related work exists which they do not focus on all parties involved within the community \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. 
%And some other work which do not focus on rationality on web services or communities involved [refrences]. 
These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in real world hurting the decision making performance.

In this paper, we introduce MLISA (Machine Learning-based Intelligent Service Agents) community framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another. This model uses the trained data in the form of information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. The training model deploys logistic regression algorithm to build hypothesis function that can thoroughly address the aforementioned research problems. Our findings show that communities of web services can efficiently find the appropriate web service to invite cooperating with them as well as a single web service can find best communities to target joining them. In further details, after being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. In contrast, communities can consider the training into account and analyze the characteristics of different individual web services and make prudent decisions while inviting a web service to join or accepting a join inquiry initiated from a web service. In general, MLISA equips web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore opting for best decision available.

In further details, MLISA is applicable for any sort of intelligent agent-based model. To effectively train web services, we used real data set (information about the data set) to extract web services' individual characteristics and used them to measure outcomes when they cooperate with one another. Engineering and extracting these features, we gathered functional and cooperative features for both individual web services and communities in 64 different time slots. We were able to investigate the path a web service might take to achieve the best utility out of effective interaction with others. All paths and the outcomes are labeled to be utilized in training model. Using cross validation set, web services are able to compute optimal hypothesis function (using logistic regression) that can be used to predict outcome out of cooperative work with other individual web services or communities. Our findings show that web services equipped with MLISA have by far better outcome in the form of cooperative service providers than the ones that either do not cooperate or randomly find communities to join.

@@

\section{The Model}\label{s:preliminaries}
In this section, we first present the architecture of MLISA. We explore the characterestics of intelligent service agents and the features we extract for training. To do this, in the following, we discuss some preliminaries.

@@

Over the past years, online services have become part of standard daily life of people around the globe. Many modern applications rely on web services from different providers. For instance, many mobile and tablet applications which have limited storage and processing power are merely interfaces aggregating different information from online services. Examples are vast, weather forecasting, ticket selling, shopping apps, local maps and places searching.

The World Wide Web Consortium (W3C) defines web services as follows: ``software system designed to support interpretable machine-to-machine interaction over a network. It has an interface described in a machine-processable format (specifically WSDL). Other systems interact with the web service in a manner prescribed by its description using SOAP messages, typically conveyed using HTTP with XML serialization in conjunction with other Web-related standards''. When developers declare a new web service, it will be
discovered based on its description that fully discloses its functionalities. Developers also have to declare a public interface and a readable documentation to help other developers when integrating different services \cite{w3cwsdl}. Nowadays, web API standards which do not require XML-based web service protocols like SOAP and WSDL are also emerging. They are also called REST (representational state transfer) services which are moving towards simpler communication protocols. 
%They are not restricted 
%to XML formats, recently JSON, a human readable and simpler format 
%is becoming popular among online service providers.

We are not going to delve into engineering details of online web service implementation and its protocols in this proposal. We are interested in web services from their business model perspective. Service providers usually charge end users for services they provide. For example, Google has listed their pricing and plans for wide range of services they provide on their web service console page\footnote{https://code.google.com/apis/console}.

In our research work, we abstract web services as rational agents\footnote{The term rational is used here in the sense that web services are utility maximizers} providing services to end users. They aim to maximize their individual income  by receiving enough requests from end users. In order to increase their revenues, web services seek for more tasks if they have the capacity and throughput to do so. Web services can join communities to have better efficiency by collaborating with others, to have access to broad market share, and to have opportunity of receiving a bigger task pool from end users. Furthermore, the high reliance on web services has increased quality expectations from end users. Communities of web services can provide higher availability, performance, reliability, and recovery for end users.

@@

The community of web services is essentially a virtual group of web services having similar and complementary functionalities. Communities aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols as single web services. Web services join communities to increase their utility by having a larger market share and task pool. Community coordinators are responsible for community development, managing membership requests from web services and distributing user tasks among the community members. Community coordinators try to attract quality web services for joining and keep the community as stable and productive as possible to gain better reputation and user satisfaction, which results in having a higher market share for the community. The way the web services reside inside communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.

@@

With a group of web services having identical or similar functionalists, QoS metrics provide nonfunctional characteristics for the optimal candidate selection. Web service quality metrics have been presented in \cite{Ardagna:2007:ASC:1263152.1263531,Menasce:2002:QIW:613357.613758,10.1109/ISSRE.2011.17}, we have adopted the most representative QoS properties of web services which highly influence the utility of web services. 
%We refer to a typical web service as ws_{i}.

@@

	\item \emph{Execution Time $(Et_{C})$} is the time a service takes to respond to various types of requests. 
	%is the expected delay between the time instant when a request is sent and the time when the result is obtained. 
	Execution time is measured in milliseconds. Execution time can be affected by load intensity, which can be measured in terms of arrival rates (such as requests per second) or number of concurrent requests. This internal feature is a positive integer. For communities the expected execution time of collaborating web services can be estimated as:

@@

The quantitative values of quality metrics need some benchmark values to represent their goodness. In other words, without some benchmark values it would be hard for web services to identify their goals, and how good or bad they would perform at any specific value of these metrics. Therefore we have introduced two external features to assess web services getting better estimate of their standing within other web services.

\begin{itemize}
  \item \emph{External Parameter 1} $(exp_1)$. is an estimate of how close the web service's \emph{execution time} is to other web services. It is the difference between web service's \emph{response time} metric and the maximum value of response time of web services, that the web service has recently gathered information about.
	\item \emph{External Parameter 2} $(exp_2)$ is a comparison of the web service's rate of performing tasks to other competing web services. It is the difference between web service's \emph{throughput} metric and the maximum value of throughput of web services, that the web service has recently gathered information about.
\end{itemize}

A community of web services are abstracted as a standard web service providing services sharing same internal and external features mentioned for web services. Inside, they adopt different protocols to manage the community, however other web services or end users can communicate with communities of web services, using standard protocols and inner details will be encapsulated for their clients.

@@

Communities of web services usually employ an implementation of Contract-Net protocol for task distribution, in which services opt for incoming tasks, and they will get the tasks if they ask for them. However in our model our community would try to distribute tasks based on their capabilities and QoS parameters the web services have announced. We have used a slightly modified \emph{weighted fair queuing} method to distribute tasks among the members of the community. The goal is to allocate incoming tasks to web services with a rate matching the throughput value of $Th_{ws}$. In the \emph{weighted fair queuing} method, the input flow is multiplexed along different paths, however in our case if the rate of incoming tasks are less than communities total throughput $(Th_{C})$ which is the summation of throughput values of the web services in the community, some of the input tasks will be queued and served with delay. 
%Thus, the amount of tasks performed by the community is $\sum_{ws}{Th_{ws}}$ when $\sum_{ws}{Th_{ws}} \leq R_{C}$. 
However, when incoming task rate is less than the throughput of the community, the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $|input Task Rate| \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each web service ($ws$) within the community.

While distributing tasks, the community members can verify the performance, throughput and quality of service of tasks being performed by web services. The community can recognize if those web services are capable of doing the amount of tasks they advertised. If for any reason there is a decline in the quality metric or throughput, the community can consider the new values as benchmark for future performance calculations, and penalize the suspicious web services. In this way, players will have incentive to truthfully reveal their real capabilities in order to profit best from the community and t  avoid being penalized. In addition, the system should be dynamic enough to detect and react to web services quality metrics variation as over time web service metrics may degrade or improve, a change that the community should adjust to.
% Therefore its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities. Also it is important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.

@@

The communities and web services earn revenue by performing tasks. The total gain is function of quality of rate of tasks being performed. The utility of a collaborative group of services $U_{C}$ is the revenue of the community. Formula \ref{u_c_normal} is an estimation of the gain of the community.

@@

The estimation can be improved specially on cases where the input task rate is high and services are under high load of tasks. The \emph{weighted fair queuing} method of task distribution would distribute tasks based on individual throughput $(Th_{w})$ value of services within community, the services with higher throughput within the community will affect the overall utility of community more since they would proportionally do more of the tasks.

@@

\subsection{The Join Challenge}\label{s:tjc}
Sometimes web services can increase their overall utility by collaborating with other web services as communities. This collaboration helps them with better ways of sharing resources, higher reputation, better market share and wider visibility. Web services and communities come with different internal and external parameters and long-term outcome is dependent on these parameters.

@@

*******SOME PARTS IS TEMPRORARY COMBINED FROM PREVIOUS WORKS*******
In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
defined communities as \emph{Service Containers} which aggregate
substitutable web services providing a common functionality (same
set of operations). They abstracted \emph{Service Containers} as
web services which are created, advertised, discovered and invoked
just as elementary web services. The \emph{Container} is
considered as a manager which is responsible for web service
selection upon receiving a request on run-time. The authors have
proposed a scoring service based on non-functional requirements of
the request and web service capabilities to dynamically chose the
web service to perform the requested task. A similar concept was
proposed by Maamar et al. in
\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
web service communities as a collection of web services with a
common functionality but different QoS properties. A community
manager, upon receiving a request, delegates the request to one of
its current members. The choice is based on the performance
history and quality metrics of each web service. The authors have
proposed an efficient global web service selection algorithm in
order to approach quality constraints and preferences for
composite services which require aggregation of different types of
services to satisfy the user.

@@

In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
autonomous web services based on coalitional game theory has been
introduced. The authors have proposed an interesting algorithm to
reach individually stable coalition partition for web services in
order to maximize their efficiency. The communities choose new web
services on the promise that it would benefit the community
without decreasing any other web service's income. In the proposed
model, the worth of community is evaluated with high emphasis on
the availability metric and considering price and cost values
only. The community structure is based on a coordination chain,
where a web service is considered as a \emph{primary} web service
and the community task-distribution method initially invokes the
primary web service and only if the primary web service is
unavailable, the method invokes the next backup web services as
they are ordered in the coordination chain. We believe that this
coordination chain limits the cooperation power as it introduces a
sort of hierarchy. However, in pure and open cooperative models,
such as the one we propose in this paper, active cooperation
activities engaging simultaneously many agents so that they can
perform the tasks more efficiently are being used. Moreover, if
the availability is high, which is the case nowadays with the
recent advancements in cloud and hardware infrastructures, the
backup web services will end-up having a very low chance of
getting jobs, especially the ones further in the chain. This will
results in a considerable waste of web services capabilities.
*******SOME PARTS IS TEMPRORARY COMBINED FROM PREVIOUS WORKS*******

>>>>

Web services are loosely-coupled business applications willing to cooperate in distributed settings within different groups called communities. Communities aim to provide web services with better visibility, efficiency, market share and total payoff. A number of mechanisms and models have been recently proposed to aggregate web
services and make them cooperate within their communities. However, the solutions mostly focus on short term goals. Moreover, these solutions generally suffer from high computational complexity, which makes decision making impossible in an on-demand fashion. In this paper, we propose a strategic decision making mechanism that regulates web service agents' decision making process in terms of cooperating with one another. This model first generates a trained set of data based on information obtained from large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. Utilizing the training model, the decision making mechanism implements a decision tree of possible viable strategies and their long-term expected utility gain.
%Utilizing the training model, the decision making mechanism implements a decision tree with an estimation of long-term utility gain for the web services. Communities can used the trained model and instantly choose best-response strategies considering their long-term gain. 
Our findings show that using this data, communities of web services can efficiently find the appropriate web service to invite cooperating with them as well as a single web service can find best communities to target joining them. In further details, after being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. In contrast, communities can consider the training into account and analyze the characteristics of different individual web services and make prudent decisions while inviting a web service to join or accepting a join inquiry initiated from a web service. In general, MLISA equips web services with efficient methods of foreseeing how their choices of actions would impact their long-term and short-term goals, therefore opting for best decision available. The experimental results show that our algorithms provide web services and community owners, in real-world-like environments, with applicable and near-perfect decision making mechanisms.

@@

\IEEEPARstart{O}{ver} the past years, online services have become an important part of many scalable business applications. The increasing reliance on online service providers has significantly influenced the way web services are engineered. Therefore, given the dynamic and unpredictable nature of the Internet, delivering high quality services is still a critical and challenging issue. One practical solution that delivers high quality service is utilizing intelligent decision making agents. These agents aim at maximizing gain by exploring the best ways to provide services that satisfy end users. However, agent-based web services are functionally limited in the sense that they cannot handle a large number of requests at the same time without compromising the quality of service provided. Recent developments have attempted to shift web services from passive models, consisting of individual components, to models made up of autonomous and group-based components that share common goals. In group-based models, interaction, composition, and cooperation are the key challenges \cite{ICWS2011-1, SCC2011-1, journals/mags/BaldoniBM10, journals/jcss/CasadoYT13} that directly impact the group's overall performance in achieving common goals. To that end, we see the emergence of web service \emph{communities}, which consist of services with similar functionality but distinct nonfunctional properties. \cite{Zeng:2003:QDW:775152.775211, Paik:2005:TSS:2229263.2230038, Medjahed05adynamic, 10.1109/ARES.2008.7}. A \emph{community} of web services runs continuous performance assessment functions that regulate web services' interactions and manage their composition and cooperation.

The advantages of community of web services are that the community facilitates the discovery of web services and a community provides better quality services compared to passive models with individual components. In other words, communities act as abstract web services, communicating with external entities via the same standard protocols that a normal web service employs. But, they regulate the service process via sophisticated internal communication protocols, thereby providing services based on the combined work of a number of web services. The down side to communities is the complexity of management involved in finding and inviting individual web services and managing the overall quality of the combined work of several web services because although they have similar functionality, they have different attitudes. When interacting with communities of web services, users send their requests to the coordinators of the community, which play the role of community representative or access point. The community coordinator in \emph{community centralized} architecture is responsible for task receive and delivery issues. Moreover, as community representative, it verifies the credentials of new web services before accepting them into the community and fires web services, that do not add enough value to the community.

Recent work has focused on the motivation and benefits of communities of web services [references]. This is due to the fact that communities facilitate discovery of web services, improve the Quality of Service (QoS), and help individual services find better market share and opportunities. However, there is a twofold challenge that has still not been addressed: (1) the first challenge is community development, which involves finding the right web services for the community, satisfying all web services and community coordinators involved within the community; and (2) the second challenge is from the individual web service's side , such that a web service seeks communities from which to obtain the best outcome. A number of proposals have attempted to address these research problems. Some of these works propose complex on-demand algorithms \cite{DBLP:conf/IEEEscc/LimTMB12, 10.1109/TSC.2012.12, 10.1109/TSC.2014.2312940} to effectively find target points, but they have to simplify the algorithm with limited parameters in order to make it feasible and algorithm executable. Simplified problems sometimes negatively influence the outcome because simplifying the constraints may cause important aspects of the problem to be ignored. For example, \cite{10.1109/TSC.2012.12} proposes a simple egalitarian way of distributing gain, which completely ignores gain for collaborative work instead of complex shapely-value. This model considers gain for all subsets of agents working together, which basically ignores the most important criteria of finding the optimal group. Other categories of related work exist that do not focus on all the parties involved within the community \cite{DBLP:conf/IEEEscc/KhosravifarABT11}. 
%And some other work which do not focus on rationality on web services or communities involved [refrences]. 
These solutions generally suffer from high complexity, which makes decision making impossible in an on-demand fashion, or they simplify important aspects to make it practical in the real world, thereby hurting the decision making performance.

In this paper, we introduce MLISA (Machine Learning-based Intelligent Service Agents) community framework that operates based on a trained model that regulates web service agents' decision making process in terms of cooperating with one another. This model uses the trained data in the form of information obtained from a large number of web services regarding their single and cooperative utilities as well as environmental parameters such as demand, service quality, etc. The training model deploys a logistic regression algorithm to build a hypothesis function that can thoroughly address the aforementioned research problems. Our findings show that communities of web services can efficiently find the appropriate web service to invite cooperating with them as well as allowing a single web service to find the best communities to join them. Furthermore, after being trained, web services get to compute expectations as utilities they would gain while cooperating with communities of different characteristics. In contrast, communities can consider the training and analyze the characteristics of different individual web services and make prudent decisions when inviting a web service to join or accepting a join inquiry initiated from a web service. In general, MLISA equips web services with efficient methods for foreseeing how their choices will impact their long-term and short-term goals; therefore, opting for best decision available.

In further detail, MLISA is applicable for any sort of intelligent agent-based model. To effectively train web services, we used real data sets (information about the data set) to extract web services' individual characteristics and used them to measure outcomes when they cooperate with one another. Engineering and extracting these features, we gathered functional and cooperative features for both individual web services and communities in 64 different time slots. We were able to investigate the path a web service might take to achieve the best utility out of effective interaction with others. All paths and the outcomes are labeled to be utilized in the training model. Using cross validation sets, web services are able to compute the optimal hypothesis function (using logistic regression) that can be used to predict outcomes of cooperative work with other individual web services or communities. Our findings show that web services equipped with MLISA have by far better outcomes in the form of cooperative service providers than the ones that either do not cooperate or randomly find communities to join.

@@

\section{The Model}\label{s:preliminaries}
In this section, we first present the architecture of MLISA. We explore the characterestics of intelligent service agents and the features we extract for training. To do this, we first discuss some preliminaries.

@@

In recent years, online services have become a standard part of daily life around the globe. Many modern applications rely on web services from different providers. For instance, many mobile and tablet applications that have limited storage and processing power are merely interfaces aggregating information from different online services. Examples are vast, including weather forecasting, ticket selling, shopping apps, local maps and location services.

The World Wide Web Consortium (W3C) defines web services as follows: ``software systems designed to support interpretable machine-to-machine interaction over a network. It has an interface described in a machine-processable format (specifically WSDL). Other systems interact with the web service in a manner prescribed by its description using SOAP messages, typically conveyed using HTTP with XML serialization in conjunction with other Web-related standards.'' When developers declare a new web service, it will be
discovered based on its description, which fully discloses its functionalities. Developers also have to declare a public interface and a readable documentation to help other developers when integrating different services \cite{w3cwsdl}. Nowadays, web API standards that do not require XML-based web service protocols like SOAP and WSDL are also emerging. They are called REST (representational state transfer) services, which are moving towards simpler communication protocols. 
%They are not restricted 
%to XML formats, recently JSON, a human readable and simpler format 
%is becoming popular among online service providers.

We are not going to delve into the engineering details of online web service implementation and its protocols in this proposal. We are interested in web services from a business model perspective. Service providers usually charge end users for services they provide. For example, Google has listed their pricing and plans for a wide range of services they provide on their web service console page\footnote{https://code.google.com/apis/console}.

In this paper, we abstract web services as rational agents\footnote{The term rational is used here in the sense that web services are utility maximizers} that provide services to end users. They aim to maximize their individual income  by receiving enough requests from end users. In order to increase their revenues, web services seek for more tasks if they have the capacity and throughput to do so. Web services can join communities to enhance efficiency by collaborating with others, to have access to broad market share, and for the opportunity to receive a bigger task pool from end users. Furthermore, the high reliance on web services has resulted in increased quality expectations from end users. Communities of web services can provide higher availability, performance, reliability, and recovery for end users.

@@

The community of web services is essentially a virtual group of web services having similar and complementary functionalities. Communities aggregate web services and communicate with other entities such as UDDI registries and users, using identical protocols to those used by single web services. Web services join communities to increase utility by having a larger market share and task pool. Community coordinators are responsible for community development, managing membership requests from web services and distributing user tasks among the community members. Community coordinators try to attract quality web services to join and keep the community as stable and productive as possible to gain a better reputation and user satisfaction, which increases the community's market share. How web services reside within communities and how communities of web services are engineered is described comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.

@@

With a group of web services having identical or similar functionalities, QoS metrics provide nonfunctional characteristics for optimal candidate selection. Web service quality metrics were presented in \cite{Ardagna:2007:ASC:1263152.1263531,Menasce:2002:QIW:613357.613758,10.1109/ISSRE.2011.17}. We have adopted the most representative QoS properties of web services that highly influence the utility of web services. 
%We refer to a typical web service as ws_{i}.

@@

	\item \emph{Execution Time $(Et_{C})$} is the time a service takes to respond to various types of requests. 
	%is the expected delay between the time instant when a request is sent and the time when the result is obtained. 
	Execution time is measured in milliseconds. Execution time can be affected by load intensity, which can be measured in terms of arrival rates (such as requests per second) or number of concurrent requests. This internal feature is a positive integer. For communities, the expected execution time of collaborating web services can be estimated as:

@@

The quantitative values of quality metrics need some benchmark values to represent their goodness. In other words, without some benchmark values it would be difficult for web services to identify their goals, and performance quality at any specific value of these metrics. Therefore, we have introduced two external features for assessing web services' estimate with regard to their standing among other web services.

\begin{itemize}
  \item \emph{External Parameter 1} $(exp_1)$. is an estimate of how close the web service's \emph{execution time} is to other web services. It is the difference between a web service's \emph{response time} metric and the maximum value of response time of web services, about which the web service has recently gathered information.
	\item \emph{External Parameter 2} $(exp_2)$ is a comparison of the web service's rate of performing tasks to other competing web services. It is the difference between a web service's \emph{throughput} metric and the maximum value of throughput of web services, about which the web service has recently gathered information.
\end{itemize}

A community of web services is abstracted as a standard web service that provides services that share the same internal and external features mentioned for web services. Inside, they adopt different protocols to manage the community; however, other web services or end users can communicate with communities of web services, using standard protocols, and inner details will be encapsulated for their clients.

@@

Communities of web services usually employ an implementation of Contract-Net protocol for task distribution, in which services opt for incoming tasks, and receive the tasks for which they ask. However, in our model, our community would try to distribute tasks based on their capabilities and the QoS parameters provided by the web services. We have used a slightly modified \emph{weighted fair queuing} method to distribute tasks among community members. The goal is to allocate incoming tasks to web services with a rate matching the throughput value of $Th_{ws}$. In the \emph{weighted fair queuing} method, the input flow is multiplexed along different paths; however, in our case, if the rate of incoming tasks is less than the community's total throughput $(Th_{C})$, which is the summation of throughput values of the web services in the community, some of the input tasks will be queued and served with a delay. 
%Thus, the amount of tasks performed by the community is $\sum_{ws}{Th_{ws}}$ when $\sum_{ws}{Th_{ws}} \leq R_{C}$. 
However, when the incoming task rate is less than the throughput of the community, the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $|input Task Rate| \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each web service ($ws$) within the community.

While distributing tasks, the community members can verify the performance, throughput and quality of service of tasks being performed by web services. The community can assess if those web services are capable of performing the number of tasks they advertised. If for any reason, there is a decline in the quality metric or throughput, the community can consider the new values as a benchmark for future performance calculations, and penalize the suspicious web services. This way, players will have incentive to truthfully disclose their actual capabilities in order to maximize profit from the community and to avoid being penalized. In addition, the system should be dynamic enough to detect and react to web services' quality metrics variation, as over time, web service metrics may degrade or improve, changes to which the community should adjust.
% Therefore its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities. Also it is important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.

@@

Communities and web services earn revenue by performing tasks. The total gain is a function of the quality of rate of tasks being performed. The utility of a collaborative group of services $U_{C}$ is the revenue of the community. Formula \ref{u_c_normal} is an estimation of the gain of the community.

@@

The estimation can be improved, especially in cases where the input task rate is high and services are experiencing high task loads. The \emph{weighted fair queuing} method of task distribution would distribute tasks based on the individual throughput $(Th_{w})$ value of services within community. The services with higher throughput will affect the overall utility of the community more because they would take on proportionately more tasks.

@@

\subsection{The Join Challenge}\label{s:tjc}
Sometimes, web services can increase their overall utility by collaborating with other web services as communities. This collaboration helps them with better ways of sharing resources, higher reputation, better market share and wider visibility. Web services and communities come with different internal and external parameters and long-term outcome is dependent on these parameters.

@@

In \cite{DBLP:journals/internet/BenatallahSD03}, Benatallah et al.
defined communities as \emph{Service Containers} which aggregate
substitutable web services providing a common functionality (same
set of operations). They abstracted \emph{Service Containers} as
web services which are created, advertised, discovered and invoked
just as elementary web services. The \emph{Container} is
considered as a manager which is responsible for web service
selection upon receiving a request on run-time. The authors have
proposed a scoring service based on non-functional requirements of
the request and web service capabilities to dynamically chose the
web service to perform the requested task. A similar concept was
proposed by Maamar et al. in
\cite{DBLP:journals/ijebr/MaamarSTBB09}. The authors introduced
web service communities as a collection of web services with a
common functionality but different QoS properties. A community
manager, upon receiving a request, delegates the request to one of
its current members. The choice is based on the performance
history and quality metrics of each web service. The authors have
proposed an efficient global web service selection algorithm in
order to approach quality constraints and preferences for
composite services which require aggregation of different types of
services to satisfy the user.

@@

In \cite{10.1109/TSC.2012.12}, a cooperative scheme among
autonomous web services based on coalitional game theory has been
introduced. The authors have proposed an interesting algorithm to
reach individually stable coalition partition for web services in
order to maximize their efficiency. The communities choose new web
services on the promise that it would benefit the community
without decreasing any other web service's income. In the proposed
model, the worth of community is evaluated with high emphasis on
the availability metric and considering price and cost values
only. The community structure is based on a coordination chain,
where a web service is considered as a \emph{primary} web service
and the community task-distribution method initially invokes the
primary web service and only if the primary web service is
unavailable, the method invokes the next backup web services as
they are ordered in the coordination chain. We believe that this
coordination chain limits the cooperation power as it introduces a
sort of hierarchy. However, in pure and open cooperative models,
such as the one we propose in this paper, active cooperation
activities engaging simultaneously many agents so that they can
perform the tasks more efficiently are being used. Moreover, if
the availability is high, which is the case nowadays with the
recent advancements in cloud and hardware infrastructures, the
backup web services will end-up having a very low chance of
getting jobs, especially the ones further in the chain. This will
results in a considerable waste of web services capabilities.
